\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[resetlabels]{multibib}

% Set margins.
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\voffset=-0.125in
\headheight=0.0in
\topmargin=0.0in
\textheight=9.0in

% Define colors.
\definecolor{addresscolor}{rgb}{0.2,0.2,0.2}
\definecolor{datecolor}{rgb}{0.5,0.5,0.5}

% Turn off page numbering.
\pagestyle{fancy}
\fancyhf{}
\lfoot{\datestyle M.A. Gully-Santiago}
\cfoot{\datestyle \thepage}
\rfoot{\datestyle September 2014}
\renewcommand{\headrulewidth}{0.0pt}

% Change font.
\renewcommand{\familydefault}{\sfdefault}

% Set parameters and content.
\newcommand{\namestyle}{\Large}
\newcommand{\deptstyle}{\footnotesize \sffamily \scshape}
\newcommand{\addressstyle}{\color{addresscolor}  \footnotesize \sffamily \upshape}
\newcommand{\datestyle}{\color{datecolor} \footnotesize \sffamily \upshape}

% Remove list labels.
\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{}

% Define bibliographies.
\newcites{j,c}{Main Products, Other Significant Products}


\begin{document}

% Print title.
    \namestyle Biographical Sketch of Michael A. Gully-Santiago \\[0.3em]
     \normalsize Citizenship: United States Citizen

\normalsize

%%%%%%
\begin{center}
 \large \textbf{Professional preparation}
\end{center}
\normalsize
%%%%%%

Boston University, Astronomy \& Physics, BA 2007

University of Texas at Austin, Astronomy, PhD- \emph{anticipated} 2015

%%%%%%
\begin{center}
 \large \textbf{Appointments}
\end{center}
\normalsize
%%%%%%

Researcher, Dept. of Astronomy UT Austin, TX $\cdot$ 2008-2014

GSRP Fellow, NASA JPL Microdevices Lab, Pasadena, CA $\cdot$ 2010-2013

Faculty member, Dexter and Southfield School, Brookline, MA $\cdot$ 2007-2008

Astronomer, Clay Center Observatory, Brookline, MA $\cdot$ 2005-2008

REU student, McDonald Observatory, Fort Davis, TX $\cdot$ 2006

Community Educator, Center for Adult Education, Brookline, MA $\cdot$ 2005-2008


\small

% Publications.
\bibliographystylej{IEEEtran}
\bibliographystylec{IEEEtran}

\nocitej{2012SPIE.8450E..2SG}
\nocitej{2011ASPC..448..633G}
\nocitej{2010SPIE.7739E..3SG}
\nocitej{2014arXiv1408.1278K}
\nocitej{2013AN....334..159J}
%\nocitec{2012SPIE.8550E..1BH}
\nocitec{2010SPIE.7739E..4LW}
%\nocitec{2010SPIE.7735E..2KL}
\nocitec{2010SPIE.7735E..1MY}
\nocitec{2010SPIE.7731E..0CG}
\bibliographyj{gullyCV}
\bibliographyc{gullyCV}

\normalsize

%%%%%%
\begin{center}
 \large \textbf{Synergistic Activities}
\end{center}
\normalsize
%%%%%%

\begin{itemize}

\item \textbf{Host, They Blinded Me with Science, a science podcast, KVRX, 91.7FM $\cdot$ Austin, TX$\cdot$ 2013--5/2014} I successfully procured seed funding from College of Natural Sciences to establish a science podcast.  I produced 30 original podcasts with $\sim3000$ collective online streams plus iTunes downloads.  I recruited guests, conducted interviews, edited audio files (with Audacity), managed digital content, authored descriptions, and posted each podcast to the web.  I promoted the show with social media.

\item \textbf{Interactive museum-style educational installation, Department of Astronomy $\cdot$ Austin, TX$\cdot$ 7/2013--9/2014}  I came up with this original outreach idea and sought collaborators.  I procured \$4.5k in funding from internally reviewed proposal.  I designed, constructed, and completed interactive display cases.  I measured over 600 user interactions since its installation.  

\item \textbf{Mentor for undergraduate student, Amanda T, Astronomy Dept., UT Austin, TX $\cdot$ 2013--2014} Trained Amanda in computer programming, data analysis, optics.

\item \textbf{Graduate Student Representative, Astronomy Dept., UT Austin, TX $\cdot$ 2011--2012} Advocate for diversity on graduate admissions committee, liaison to faculty, ombudsman, delegate for University-wide Graduate Student Assembly.

\item \textbf{Founder of cofounding member of ATXastroML, AstroData group, and D.A.T.A group}  I have been promoting interdisciplinary interactions among graduate students in statistics, computer science, biology, etc.  All of my research materials are posted to GitHub, a code sharing website.

\end{itemize}
	

%%%%%%
 \large \underline{Collaborators}
\normalsize
%%%%%%

Allers, Katelyn (Bucknell U.); Deen, Casey (MPIA); Kendrew, Sarah (Oxford U.); Pak, Soojong (Kyung Hee University); Weinberger, Alycia (Carnegie Institute of Washington);  

Thesis Advisor: Daniel T. Jaffe

Proposed Postdoctoral Sponsor: Kelle Cruz

\end{document}
